---
title: "Assignment 07: Web Scraping the FSB Directory"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
    code_folding: show
    df_print: kable
    self_contained: true
    mathjax: null
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

This code uses the function and `purrr` approach from Class 11 to collect
the department, name, position, and website for faculty and staff in all
seven departments.

## Scrape the directory

```{r purrr}
# Department names as they appear in the directory URLs.
dept_names = c(
  'Accountancy', 'Economics', 'Entrepreneurship', 'Finance',
  'Information Systems -- Analytics', 'Marketing', 'Management'
)

# This function takes a department as input and returns a data frame.
scrape_fsb_directory = function(dept){
  directory_url = paste0(
    'https://miamioh.edu/fsb/directory/?up=/query/all/all/',
    utils::URLencode(dept), '/all'
  )

  # Pause between requests, then read the webpage.
  Sys.sleep(1)
  webpage = rvest::read_html(directory_url)

  # Keep each person's information together in the same table cell.
  webpage |> rvest::html_elements("#sidebar-main table td:nth-child(3)") -> people
  people |> rvest::html_element("strong a") -> name_links

  # html_text() keeps hidden HTML comments out of the names.
  name_links |> rvest::html_text(trim = TRUE) |> stringr::str_squish() -> faculty_names
  people |> rvest::html_element("i") |> rvest::html_text2() |>
    stringr::str_squish() -> positions
  name_links |> rvest::html_attr("href") -> websites

  df = data.frame(
    department = gsub(" -- ", " & ", dept, fixed = TRUE),
    name = faculty_names,
    position = positions,
    website = websites
  )
  return(df)
}

# .x is the vector to iterate over, and .f is the function to use.
fsb_directory = purrr::map_df(.x = dept_names, .f = scrape_fsb_directory)
```

## First few observations

```{r first-observations}
head(fsb_directory)
```

## Check the results

The department counts show that all seven departments are included.

```{r department-counts}
dplyr::count(fsb_directory, department, name = "people")
```

The checks below confirm that all seven expected departments are present
and that every row has a department, name, position, and website. A zero
in the last output means that column has no missing or blank values.

```{r check-completeness}
setequal(
  unique(fsb_directory$department),
  gsub(" -- ", " & ", dept_names, fixed = TRUE)
)

colSums(is.na(fsb_directory) | fsb_directory == "")
```

Source: [Miami University FSB Directory](https://miamioh.edu/fsb/directory/).
