---
title: "Class_011"
author: "Kyle Dodson"
date: "2026-09-30"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    code_download: true
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Learning Objectives

- Enable you to scrape multiple web pages (from the same site), using a `for` loop type approach.

- Enable you to scrape multiple webpages (from the same site), using the [purrr package](https://purrr.tidyverse.org/), which is a functional programming approach.
*NOTE:* In this process, we will create our own function.

## Re-examining the bulletin example

Let us try to expand on the example from last class to include the following:
[ACC](https://bulletin.miamioh.edu/courses-instruction/acc/),
[BUS](https://bulletin.miamioh.edu/courses-instruction/bus/),
[ISA](https://bulletin.miamioh.edu/courses-instruction/isa/), and
[MKT](https://bulletin.miamioh.edu/courses-instruction/mkt/).

**CCOMMENT** obviously, you can repeat your code few times with changing the URL. This will work for a few links but would be quite tedious for large amounts of scraping. We will follow the **DRY PRINCIPLE**, which stands for **Don't Repeat Yourself**

```{r bulletin}
dept_abbrv = c('acc', 'bus', 'isa', 'mkt')

courses_df = data.frame() # initializing a container to store stuff in from the loop
for (abbrv in dept_abbrv) {
  cat( rep("-", 50) , "/n" )
  print(abbrv)
  bulletin_url = paste0(
  'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/'
)

# [Q] Why did Fadel make this an R object instea dof a string like last class?
# [A] we did this so we can reuse the rest of our code with only changing the URL
webpage = rvest::read_html(bulletin_url)

webpage |> rvest::html_elements("strong") |> rvest::html_text2() -> titles
webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs

df = data.frame(title = titles, desc = descs)
print(df$title[1:2])
courses_df = rbind(courses_df, df)
}

```


## `purrr` approach for the same problem

This is a funtional programming approach, and we will write our own function. In R, we use a function called `function` to create a function. As opposed to Python, R functions return a single object.

```{r purrr}
#This function takes an abbrev as an input and returns a data_frame as an output
scrape_mu_bulletin = function(abbrv){
  bulletin_url = paste0(
  'https://bulletin.miamioh.edu/courses-instruction/', abbrv, '/'
)

# [Q] Why did Fadel make this an R object instea dof a string like last class?
# [A] we did this so we can reuse the rest of our code with only changing the URL
webpage = rvest::read_html(bulletin_url)

webpage |> rvest::html_elements("p.courseblocktitle") |> rvest::html_text2() -> titles
webpage |> rvest::html_elements("p.courseblockdesc") |> rvest::html_text2() -> descs

df = data.frame(title = titles, desc = descs)
}

test = scrape_mu_bulletin(abbrv = 'eco')

# to use functions from purrr, we will use a map_*(), or map2_*(), or a pmap_*()
# map uses a function that takes a single input (or you are only changing a single input)
# map2 uses a unction that takes 2 inputs
# pmap >=3
# after the _, you put the type of object you are getting back

# the .x is the vector that we will iterate over
# and the .f is the function we use

courses_df_from_purrr = purrr::map_df(.x = dept_abbrv, .f = scrape_mu_bulletin)
```


## Scrape data from the website planecrashinfo

The website that we want to scrape is called: <https://www.planecrashinfo.com/> and it contains the database of plane crashes by year.

```{r}
year = 2025

crash_url = paste0('https://www.planecrashinfo.com/', year, '/', year, 'htm')

crash_page = rvest::read_html(crash_url)
```






