---
title: "Assignment 06: Airbnb Market Analysis with dplyr"
output:
  html_document:
    toc: true
    toc_depth: 2
    self_contained: true
---

The analysis compares Chicago, Columbus, and the Twin Cities. Prices come from
the listings table. Unavailable nights may be booked or blocked by the host.
Monthly reviews are a measure of demand, not a count of bookings, and estimated
revenue is modeled rather than actual reported revenue.

```{r setup, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(width = 120, pillar.sigfig = 8, tibble.width = Inf)

con = DBI::dbConnect(RSQLite::SQLite(), "../data/midwest_airbnb_extended.db")
listings     = DBI::dbReadTable(con, "listings") |> tibble::as_tibble()
availability = DBI::dbReadTable(con, "availability_monthly") |> tibble::as_tibble()
reviews      = DBI::dbReadTable(con, "reviews_monthly") |> tibble::as_tibble()
DBI::dbDisconnect(con)
```

## Task 1

Count each host's listings across all three cities before calculating city shares.

```{r task1}
host_counts = listings |>
  dplyr::count(host_id, name = "host_listings")

listings_with_hosts = listings |>
  dplyr::left_join(host_counts, by = "host_id")

A1 = host_counts |>
  dplyr::filter(host_listings >= 10) |>
  dplyr::summarize(hosts_10_plus = dplyr::n()) |>
  dplyr::pull(hosts_10_plus)

ownership_by_city = listings_with_hosts |>
  dplyr::group_by(city) |>
  dplyr::summarize(
    total_listings = dplyr::n(),
    listings_with_large_hosts = sum(host_listings >= 10, na.rm = TRUE),
    large_host_share_pct = 100 * mean(host_listings >= 10, na.rm = TRUE),
    .groups = "drop"
  )

A2 = ownership_by_city |>
  dplyr::filter(city == "Chicago") |>
  dplyr::pull(large_host_share_pct) |>
  round(1)

ownership_by_city
data.frame(A1 = A1, A2 = A2)
```

## Task 2

Find the lowest median price per person among qualifying Columbus neighbourhoods.

```{r task2}
family_value = listings |>
  dplyr::filter(
    room_type == "Entire home/apt",
    accommodates >= 4,
    number_of_reviews >= 10,
    review_scores_rating >= 4.8
  ) |>
  dplyr::mutate(price_per_person = price / accommodates) |>
  dplyr::group_by(city, neighbourhood) |>
  dplyr::summarize(
    qualifying_listings = dplyr::n(),
    median_price_per_person = median(price_per_person, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::filter(qualifying_listings >= 20)

columbus_value = family_value |>
  dplyr::filter(city == "Columbus") |>
  dplyr::arrange(median_price_per_person)

A3 = columbus_value |>
  dplyr::slice_head(n = 1) |>
  dplyr::pull(neighbourhood)

columbus_value
data.frame(A3 = A3)
```

## Task 3

Use one summarize call with across to calculate all three medians.

```{r task3}
earnings_by_type = listings |>
  dplyr::group_by(city, room_type) |>
  dplyr::summarize(
    dplyr::across(
      c(price, reviews_per_month, estimated_revenue_l365d),
      ~ median(.x, na.rm = TRUE),
      .names = "median_{.col}"
    ),
    .groups = "drop"
  )

A4 = earnings_by_type |>
  dplyr::filter(city == "Twin Cities", room_type == "Entire home/apt") |>
  dplyr::pull(median_estimated_revenue_l365d)

earnings_by_type
data.frame(A4 = A4)
```

## Task 4

Round the top-ten-percent cutoff up within each city, keeping exactly that many rows.

```{r task4}
ranked_listings = listings |>
  dplyr::group_by(city) |>
  dplyr::arrange(dplyr::desc(estimated_revenue_l365d), .by_group = TRUE) |>
  dplyr::mutate(
    top_10_percent = dplyr::row_number() <= ceiling(0.10 * dplyr::n())
  )

revenue_concentration = ranked_listings |>
  dplyr::summarize(
    total_listings = dplyr::n(),
    top_10_listings = sum(top_10_percent),
    total_estimated_revenue = sum(estimated_revenue_l365d, na.rm = TRUE),
    top_10_estimated_revenue = sum(
      estimated_revenue_l365d[top_10_percent], na.rm = TRUE
    ),
    top_10_revenue_share_pct =
      100 * top_10_estimated_revenue / total_estimated_revenue,
    .groups = "drop"
  )

A5 = revenue_concentration |>
  dplyr::filter(city == "Columbus") |>
  dplyr::pull(top_10_revenue_share_pct) |>
  round(1)

concentration_for_B2 = ownership_by_city |>
  dplyr::select(city, large_host_share_pct) |>
  dplyr::inner_join(
    revenue_concentration |>
      dplyr::select(city, top_10_revenue_share_pct),
    by = "city"
  ) |>
  dplyr::mutate(
    dplyr::across(
      c(large_host_share_pct, top_10_revenue_share_pct),
      ~ round(.x, 1)
    )
  )

revenue_concentration
concentration_for_B2
data.frame(A5 = A5)
```

## Task 5

The denominator includes entire homes with October calendar data. Mostly taken
means less than half of the month's nights are available; it does not establish
whether those nights are booked or blocked.

```{r task5}
october_entire_homes = availability |>
  dplyr::filter(month == "2026-10") |>
  dplyr::inner_join(
    listings |>
      dplyr::filter(room_type == "Entire home/apt") |>
      dplyr::select(id, city),
    by = "id"
  ) |>
  dplyr::mutate(mostly_taken = nights_available < 0.5 * nights_in_month)

october_by_city = october_entire_homes |>
  dplyr::group_by(city) |>
  dplyr::summarize(
    entire_homes = dplyr::n(),
    mostly_taken_homes = sum(mostly_taken, na.rm = TRUE),
    mostly_taken_share_pct = 100 * mean(mostly_taken, na.rm = TRUE),
    .groups = "drop"
  ) |>
  dplyr::arrange(mostly_taken_share_pct)

lowest_october_share = october_by_city |>
  dplyr::slice_head(n = 1)

A6 = lowest_october_share |> dplyr::pull(city)
A7 = lowest_october_share |>
  dplyr::pull(mostly_taken_share_pct) |>
  round(1)

october_by_city
data.frame(A6 = A6, A7 = A7)
```

## Task 6

Use July 2025 through June 2026, inclusive, and add the reviews within each city and month.

```{r task6}
reviews_by_city_month = reviews |>
  dplyr::inner_join(
    listings |> dplyr::select(id, city),
    by = "id"
  ) |>
  dplyr::filter(month >= "2025-07", month <= "2026-06") |>
  dplyr::group_by(city, month) |>
  dplyr::summarize(
    total_reviews = sum(reviews, na.rm = TRUE),
    .groups = "drop"
  )

twin_cities_monthly = reviews_by_city_month |>
  dplyr::filter(city == "Twin Cities") |>
  dplyr::arrange(dplyr::desc(total_reviews))

A8 = twin_cities_monthly |>
  dplyr::slice_head(n = 1) |>
  dplyr::pull(month)

A9 = twin_cities_monthly |>
  dplyr::summarize(ratio = max(total_reviews) / min(total_reviews)) |>
  dplyr::pull(ratio) |>
  round(2)

print(twin_cities_monthly, n = 12)
data.frame(A8 = A8, A9 = A9)
```

## Task 7

Compare entire homes with known Superhost status. Reviews per month provide a
second measure for the advice in B1. These group comparisons do not establish
what gaining the badge would cause for an individual listing.

```{r task7}
superhost_summary = listings |>
  dplyr::filter(
    room_type == "Entire home/apt",
    host_is_superhost %in% c("t", "f")
  ) |>
  dplyr::group_by(city, host_is_superhost) |>
  dplyr::summarize(
    listings = dplyr::n(),
    median_price = median(price, na.rm = TRUE),
    median_rating = median(review_scores_rating, na.rm = TRUE),
    median_reviews_per_month = median(reviews_per_month, na.rm = TRUE),
    .groups = "drop"
  )

superhost_premiums = superhost_summary |>
  dplyr::filter(host_is_superhost == "t") |>
  dplyr::select(city, superhost_median_price = median_price) |>
  dplyr::inner_join(
    superhost_summary |>
      dplyr::filter(host_is_superhost == "f") |>
      dplyr::select(city, other_host_median_price = median_price),
    by = "city"
  ) |>
  dplyr::mutate(premium_dollars = superhost_median_price - other_host_median_price)

superhost_summary
superhost_premiums
```

## Task 8

Find listings with no matching ID anywhere in the availability table.

```{r task8}
missing_availability = listings |>
  dplyr::anti_join(availability, by = "id")

A10 = missing_availability |>
  dplyr::summarize(missing_listings = dplyr::n()) |>
  dplyr::pull(missing_listings)

missing_by_city = missing_availability |>
  dplyr::count(city, name = "missing_listings", sort = TRUE)

missing_by_city
data.frame(A10 = A10)
```
